\clearpage{\pagestyle{empty}\cleardoublepage}

\begin{thebibliography}{3}

\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{fluo} Waters, J.C., and Swedlow, J.R. (2007), \emph {"Interpreting Fluorescence Microscopy Images and Measurements. In Evaluating Techniques in Biochemical Research"} \newline D. Zuk, ed. (Cambridge, MA: Cell Press), \newline http://www.cellpress.com/misc/page?page=ETBR.

\bibitem{storia} Marco Brusadin (2010), \emph{"La microscopia in fluorescenza"} \newline  http://www.marcobrusadin.it

\bibitem{quenching} F.W.D. Rost (1996), \emph{"Fluorescence microscopy"} \newline ed. Cambridge University Press

\bibitem{tecniche} J.B. Pawley (2006), \emph{"Handbook of biological confocal microscopy"} \newline ed. Springer

\bibitem{NA} M.E. Dailey, A. Khodjakov, C.L. Rieder, M. Platani, J.R. Swedlow, P.D. Andrews, Yu-li Wang, J.C. Waters, N.S. Claxton, S.G. Olenych, J.D. Griffin and M.W. Davidson, \emph{"Optical system and detector requirements for live-cell imaging"} \newline http://www.microscopyu.com/articles/livecellimaging/imagingsystems.html

\bibitem{Nikon1} M.W. Davidson, K.R. Spring (2006), \emph{"Introduction to fluorescence microscopy - Nikon microscopy, the source for microscopy education"} \newline [Online; accessed 15-October-2010, Nikon]

\bibitem{Nikon2} S.A. Schwartz, M.W. Davidson, J.S. Silfies, E.G. Lieser (2010), \emph{"Nikon perfect focus system - Nikon microscopy, the source for microscopy education"} \newline [Online; accessed 19-October-2010, Nikon]

\bibitem{difetti} G. Pietro Sini, Donato Di Ferdinando, Gabriele Sirri (2013), \emph{"Problemi tecnici della microscopia ottica"} \newline http://www.funsci.com/fun3\_it/sini/mo/m\_ottica.htm

\bibitem{nigro} P. Mazzoldi, M. Nigro, C. Voci (2007), \emph{"Fisica - Volume II"} \newline ed. EdiSES

\bibitem{decon} Dr. David S.C. Biggs (2004), \emph{"Biophotonics International, photonic solutions for biotechnology and medicine - Clearing Up Deconvolution"} \newline ed. Laurin Publishing Co. Inc.

\bibitem{python} A. Downey, J. Elkner, C. Meyers (2002), \emph{"How to Think Like a Computer Scientist - Learning with Python"} \newline Green Tea Press, Wellesley (Massachusetts)

\end{thebibliography} 